Making Sequential Programs Deterministic

### 2019-03-28 design.tex
Change more \ref to \cref

\Cref{fig-poly-resolution} presents the rule for type checking of methods annotated with \<PolyDet> or its variants.
A polymorphic method type checks if every instantiation of \<PolyDet> type checks. If this method has \<PolyDet>$\uparrow$ or \<PolyDet>$\downarrow$
in its signature then the instantiation of \<PolyDet> at that location gets replaced by the appropriate type as shown in Table~\ref{tab-poly-resolutions}.

@@

With the above rules, \theDeterminismChecker will automatically annotate a local collection with type \<NonDet> and its
type arguments will get the type qualifier \<Det>. For example, a locally declared \codeid{List} of \codeid{Strings} will be automatically annotated
as \codeid{NonDet List<Det String>}. Recall from~\ref{collection-rules} that \theDeterminismChecker does not allow this type on
any collection. While this is still sound, it will result in \theDeterminismChecker reporting a lot of errors because every locally declared 
collection gets annotated with this invalid type. To avoid this situation, we make an exception to the defaulting rules for local collections
and annotate their type parameters also with \<NonDet>. So a local list of Strings gets the default qualifier of \codeid{NonDet List<NonDet String>}. While this defaulting eliminates the possibility of automatically annotating locals collections with an invalid
type, it could result in a high number of false positives. In the following code snippet,
\begin{verbatim}
void test(@Det List<@Det String> argList) {
    List<String> localList = argList;
}    
\end{verbatim}
\theDeterminismChecker would report an error at the assignment statement since the inferred type for \codeid{localList} is 
\codeid{NonDet List<NonDet> String} and since collections types are invariant.
We therefore recommend that programmers explicitly annotate
all local variables that are collections to reduce false positives.

@@

%as \codeid{@NonDet List<@Det String>}. Recall from~\ref{collection-rules} that \theDeterminismChecker does not allow this type on

>>>>

\Cref{fig-poly-resolution} presents the rule for type checking of methods annotated with \<PolyDet> or its variants.
A polymorphic method type checks if every instantiation of \<PolyDet> type checks. If this method has \<PolyDet>$\uparrow$ or \<PolyDet>$\downarrow$
in its signature then the instantiation of \<PolyDet> at that location gets replaced by the appropriate type as shown in \cref{tab-poly-resolutions}.

@@

With the above rules, \theDeterminismChecker will automatically annotate a local collection with type \<NonDet> and its
type arguments will get the type qualifier \<Det>. For example, a locally declared \codeid{List} of \codeid{Strings} will be automatically annotated
as \codeid{NonDet List<Det String>}. Recall from~\cref{collection-rules} that \theDeterminismChecker does not allow this type on
any collection. While this is still sound, it will result in \theDeterminismChecker reporting a lot of errors because every locally declared 
collection gets annotated with this invalid type. To avoid this situation, we make an exception to the defaulting rules for local collections
and annotate their type parameters also with \<NonDet>. So a local list of Strings gets the default qualifier of \codeid{NonDet List<NonDet String>}. While this defaulting eliminates the possibility of automatically annotating locals collections with an invalid
type, it could result in a high number of false positives. In the following code snippet,
\begin{verbatim}
void test(@Det List<@Det String> argList) {
    List<String> localList = argList;
}    
\end{verbatim}
\theDeterminismChecker would report an error at the assignment statement since the inferred type for \codeid{localList} is 
\codeid{NonDet List<NonDet> String} and since collections types are invariant.
We therefore recommend that programmers explicitly annotate
all local variables that are collections to reduce false positives.

@@

%as \codeid{@NonDet List<@Det String>}. Recall from~\cref{collection-rules} that \theDeterminismChecker does not allow this type on
